Naturalness in U(1) extensions of the MSSM

### 2014-11-12 paper/e6ssm-tuning-paper.tex
Fixed/clarified status of RGEs in code, added a reference to Martin's RGE paper, shortened bibtex entries for some of the XENON100 papers

Using the approach outlined above, we have scanned the low energy parameter space of the MSSM and E$_6$SSM and calculated the fine tuning in each of the models considered. To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}. In order to include effects coming from 2-loop RG running, the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba} were used instead of the 1-loop results that had previously been implemented. The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs}. To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant 1- and 2-loop corrections to the CP-even Higgs masses were included. The parameter ranges that were scanned over are presented in Table \ref{tab:scanranges}. With the exception of the stop mixing $A_t$, which was logarithmically scanned, all parameters were linearly scanned. In order to ensure the validity of the approximate RGE solutions, the input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models. Finally, the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$. 

@@

>>>>

Using the approach outlined above, we have scanned the low energy parameter space of the MSSM and E$_6$SSM and calculated the fine tuning in each of the models considered. To do so, we implemented the above expressions for computing the fine tuning in a modified version of the E$_6$SSM spectrum generator that was used in \cite{Athron:2013ipa}. This code implemented 2-loop RGEs for all parameters except the soft scalar masses. In order to properly include the fine tuning impact of the $SU(3)$ gaugino soft mass $M_3$, we have extended the original code to make use of the 2-loop RGEs generated by SARAH \cite{Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta} and FlexibleSUSY \cite{Athron:2014yba}. The CP-even Higgs masses are calculated including the leading 1-loop effective potential contributions given in \cite{Athron:2009bs} and the leading 2-loop contributions. To scan over the MSSM parameter space, the equivalent MSSM fine tuning expressions were implemented into a modifed version of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For consistency with the results produced in the $E_6$ models, and for computational speed, for our main scans only the dominant 1- and 2-loop corrections to the CP-even Higgs masses were included. The parameter ranges that were scanned over are presented in Table \ref{tab:scanranges}. With the exception of the stop mixing $A_t$, which was logarithmically scanned, all parameters were linearly scanned. All other parameters were decoupled by setting the remaining soft masses to values of $5$ TeV, while the first and second generation Yukawa couplings and their associated soft trilinears were taken to vanish. The $U(1)$ gaugino soft mass $M_1$ was fixed to $M_1=300$ GeV, and we fix $M_3=2000$ GeV. The input scale $M_X$ was set to $M_X=20$ TeV for both the MSSM and the $E_6$ models. Finally, the fine tuning was evaluated at the scale $Q=M_{\textrm{SUSY}}=\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q=M_{\textrm{SUSY}}$. 

@@

Provided that one does not run over the too large a range of scales, the solutions to the
RG equations for a model can be reasonably well approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).
Computing the first few terms of the series requires only the 1- and 2-loop RGEs, which are well known for
the MSSM and may be obtained from general results \cite{Martin:1993zk} for other models.
